---
title: "The impact of Covid-19 on firms' productivity and markups: models"
author: "Jérémy Feteira"
date: ""
lang: fr
output:
 pdf_document:
    df_print: kable
    keep_tex: yes
    number_section: yes
    toc: yes
 rmdformats::readthedown:
   gallery: no
   highlight: tango
   lightbox: yes
   self_contained: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r package}
library(readxl)
library(plm)
library(dplyr)
library(tidyr)
library(kableExtra)
library(stargazer)
library(lmtest)
```

```{r}
# si above = TRUE on a un header_above
tab_fun <- function(tab, above = FALSE, title = title, font_size = 10, header = NULL){
  if(above){
    tab %>% kable(caption = title) %>%
    kable_styling(font_size = font_size, full_width=FALSE, stripe_color = "lightgray", stripe_index = 0,
                  latex_options = c("HOLD_position", "striped"), position = "center") %>%
    add_header_above(header = header, bold=TRUE, color="red")%>%
    column_spec(1, bold=T) %>%
    row_spec(0, bold=T)
  } else {
    tab %>% kable(caption = title) %>%
      kable_styling(font_size = font_size, full_width=FALSE, stripe_color = "lightgray", stripe_index = 0,
                    latex_options = c("HOLD_position", "striped"), position = "center") %>%
      column_spec(1, bold=T) %>%
      row_spec(0, bold=T)
  }
}

################# Matrice de Cramer pour corrplot ############################################
cv <- function(x, y) {
  t <- table(x, y)
  chi <- suppressWarnings(chisq.test(t))$statistic
  cramer <- sqrt(chi / (length(x) * (min(dim(t)) - 1)))
  cramer
}

cramer.matrix<-function(y, fill = TRUE){
  col.y<-ncol(y)
  V<-matrix(ncol=col.y,nrow=col.y)
  for(i in 1:(col.y - 1)){
    for(j in (i + 1):col.y){
      V[i,j]<-cv(pull(y,i),pull(y,j))
    }
  }
  diag(V) <- 1 
  if (fill) {
    for (i in 1:ncol(V)) {
      V[, i] <- V[i, ]
    }
  }
  colnames(V)<-names(y)
  rownames(V)<-names(y)
  V
}
```

# Introduction

```{r}
setwd("D:/Comission_europeenne")
data <- read_excel("data_perso.xlsx")

data[c(6:26, 28:37)] <- sapply(data[c(6:26, 28:37)],as.numeric)
data$Country <- as.factor(data$Country)

## we create the variable period: Quarter-Year
data <- data %>% unite(Period, c(Quarter, Year), sep = "-", remove = FALSE)
data <- data[,-c(2, 4:6, 28, 39)]
```

```{r}
data <- data %>% rename(
  school_closing=`C1_School closing`, worplace_closing=`C2_Workplace closing`,
  cancel_public_events=`C3_Cancel public events`, close_public_transport=`C5_Close public transport`, 
  restrictions_on_gathering=`C4_Restrictions on gatherings`,
  stay_at_home_requirements=`C6_Stay at home requirements`,
  restrictions_on_internal_movement=`C7_Restrictions on internal movement`,
  international_travel_controls=`C8_International travel controls`,
  income_support=`E1_Income support`,
  public_information_campaings=`H1_Public information campaigns`,
  testing_policy=`H2_Testing policy`, contact_tracing=`H3_Contact tracing`,
  emergency_investment_in_healthcare=`H4_Emergency investment in healthcare`,
  investment_in_vaccines=`H5_Investment in vaccines`,
  facial_coverings=`H6_Facial Coverings`, vaccination_policy=`H7_Vaccination policy`
)
```


First, we delete the rows that have missing values:

```{r}
data_bis <- na.omit(data)
data_bis <- droplevels(data_bis)
data_bis$Period <- as.factor(data_bis$Period)
```

## Cylinder panel

We verify that we have a cylinder panel:

```{r}
cyl <- pdim(data_bis)
cyl_tab <- cbind(cyl$nT[1], cyl$nT[2], cyl$balanced)
colnames(cyl_tab) <- c("Countries", "Period", "Cylinder")
rownames(cyl_tab) <- c("Value")
tab_fun(cyl_tab, title = "Description of the panel")
```

```{r}
table(data_bis$Country)
```

The panel is not cylinder. This is due at Korea which has only 28 values out of 84. So I removed it:

```{r}
data_bis <- data_bis[!data_bis$Country=="Korea",]
data_bis <- droplevels(data_bis)
```

```{r}
cyl <- pdim(data_bis)
cyl_tab <- cbind(cyl$nT[1], cyl$nT[2], cyl$balanced)
colnames(cyl_tab) <- c("Countries", "Period", "Cylinder")
rownames(cyl_tab) <- c("Value")
tab_fun(cyl_tab, title = "Description of the panel")
```

Now, we have 84 periods by country and 24 countries.

# Model for stringency index by productivity for each sector

## Heterogeneity test

First, we test the pooling model versus the within model with the Chow test.

```{r}
model_stringency <- StringencyIndex ~ agriculture_forestry_fishing_euro + other_service_activities_euro +
  construction_euro + financial_insurance_euro + industry_no_construction_euro + 
  information_communication_euro + public_defence_education_health_social_euro +
  professionnal_scientific_technical_administrative_support_euro + 
  real_estate_euro + wholesale_retail_transport_accomodation_food_euro
```

```{r}
pooling_model_stringency <- plm(model_stringency, data = data_bis, model = "pooling", 
                                index=c("Country", "Period"))
within_model_stringency <- plm(model_stringency, data = data_bis, model = "within", 
                               index=c("Country", "Period"))
pooltest(pooling_model_stringency, within_model_stringency)
```

The p-value is strictly below 0.01, so we reject $H_0$, the within model is strictly better than the pooling model.

Now we test the within model against the random effect model using the Hausman test:

```{r}
random_model_stringency <- plm(model_stringency, data = data_bis, model = "random", 
                               index=c("Country", "Period"))
phtest(within_model_stringency, random_model_stringency)
```

Because the p-value is lower than 0.01, we reject $H_0$, the within model is strictly better than the random model.

## Heteroskedasticity

Now, we need to check if our within model has heteroskedasticity:

```{r}
bptest(within_model_stringency)
```

The p-value is strictly under 0.05, so we reject $H_0$ which means that the variant is not constant accross individuals. We have heteroskedasticity.

We will correct heteroskedasticity:

```{r}
data_bis$residuals_stringency <- within_model_stringency$residuals
varfunc.ols2 <- plm(log(residuals_stringency^2) ~ log(agriculture_forestry_fishing_euro) +
                      log(other_service_activities_euro) + log(construction_euro) +
                      log(financial_insurance_euro) + log(industry_no_construction_euro) +
                      log(information_communication_euro) +
                      log(public_defence_education_health_social_euro) +
                      log(professionnal_scientific_technical_administrative_support_euro) + 
                      log(real_estate_euro) + log(wholesale_retail_transport_accomodation_food_euro),
                    data=data_bis, model="within")

data_bis$varfunc2 <- exp(varfunc.ols2$model[1,1])

within_model_stringency <- plm(model_stringency, data = data_bis, model = "within", 
                               index=c("Country", "Period"), weights = 1/sqrt(varfunc2))
```

## Final model

The final model with stringency index a

```{r}
stargazer(within_model_stringency, type="text")
```



# Model for government response index by productivity for each sector

## Heterogeneity test

First, we test the pooling model versus the within model with the Chow test.

```{r}
model_government <- GovernmentResponseIndex ~ agriculture_forestry_fishing_euro +
  other_service_activities_euro + construction_euro + financial_insurance_euro +
  industry_no_construction_euro + information_communication_euro +
  public_defence_education_health_social_euro +
  professionnal_scientific_technical_administrative_support_euro + 
  real_estate_euro + wholesale_retail_transport_accomodation_food_euro
```

```{r}
pooling_model_government <- plm(model_government, data = data_bis, model = "pooling", 
                                index=c("Country", "Period"))
within_model_government <- plm(model_government, data = data_bis, model = "within", 
                               index=c("Country", "Period"))
pooltest(pooling_model_government, within_model_government)
```

The p-value is strictly below 0.01, so we reject $H_0$, the within model is strictly better than the pooling model.

Now we test the within model against the random effect model using the Hausman test:

```{r}
random_model_government <- plm(model_government, data = data_bis, model = "random", 
                               index=c("Country", "Period"))
phtest(within_model_government, random_model_government)
```

Because the p-value is lower than 0.01, we reject $H_0$, the within model is strictly better than the random model.

## Heteroskedasticity

Now, we need to check if our within model has heteroskedasticity:

```{r}
bptest(within_model_government)
```

The p-value is strictly under 0.05, so we reject $H_0$ which means that the variant is not constant accross individuals. We have heteroskedasticity.

We will correct heteroskedasticity:

```{r}
data_bis$residuals_government <- within_model_government$residuals
varfunc.ols2 <- plm(log(residuals_government^2) ~ log(agriculture_forestry_fishing_euro) +
                      log(other_service_activities_euro) + log(construction_euro) +
                      log(financial_insurance_euro) + log(industry_no_construction_euro) +
                      log(information_communication_euro) +
                      log(public_defence_education_health_social_euro) +
                      log(professionnal_scientific_technical_administrative_support_euro) + 
                      log(real_estate_euro) + log(wholesale_retail_transport_accomodation_food_euro),
                    data=data_bis, model="within")

data_bis$varfunc2 <- exp(varfunc.ols2$model[1,1])

within_model_government <- plm(model_government, data = data_bis, model = "within", 
                               index=c("Country", "Period"), weights = 1/sqrt(varfunc2))
```

## Final model

```{r}
stargazer(within_model_government, type="text")
```


# Model for containment and health index by productivity for each sector

## Heterogeneity test

First, we test the pooling model versus the within model with the Chow test.

```{r}
model_containment <- ContainmentHealthIndex ~ agriculture_forestry_fishing_euro +
  other_service_activities_euro + construction_euro + financial_insurance_euro +
  industry_no_construction_euro + information_communication_euro +
  public_defence_education_health_social_euro +
  professionnal_scientific_technical_administrative_support_euro + 
  real_estate_euro + wholesale_retail_transport_accomodation_food_euro
```

```{r}
pooling_model_containment <- plm(model_containment, data = data_bis, model = "pooling", 
                                index=c("Country", "Period"))
within_model_containment <- plm(model_containment, data = data_bis, model = "within", 
                               index=c("Country", "Period"))
pooltest(pooling_model_containment, within_model_containment)
```

The p-value is strictly below 0.01, so we reject $H_0$, the within model is strictly better than the pooling model.

Now we test the within model against the random effect model using the Hausman test:

```{r}
random_model_containment <- plm(model_containment, data = data_bis, model = "random", 
                               index=c("Country", "Period"))
phtest(within_model_containment, random_model_containment)
```

Because the p-value is lower than 0.01, we reject $H_0$, the within model is strictly better than the random model.

## Heteroskedasticity

Now, we need to check if our within model has heteroskedasticity:

```{r}
bptest(within_model_containment)
```

The p-value is strictly under 0.05, so we reject $H_0$ which means that the variant is not constant accross individuals. We have heteroskedasticity.

We will correct heteroskedasticity:

```{r}
data_bis$residuals_containment <- within_model_containment$residuals
varfunc.ols2 <- plm(log(residuals_containment^2) ~ log(agriculture_forestry_fishing_euro) +
                      log(other_service_activities_euro) + log(construction_euro) +
                      log(financial_insurance_euro) + log(industry_no_construction_euro) +
                      log(information_communication_euro) +
                      log(public_defence_education_health_social_euro) +
                      log(professionnal_scientific_technical_administrative_support_euro) + 
                      log(real_estate_euro) + log(wholesale_retail_transport_accomodation_food_euro),
                    data=data_bis, model="within")

data_bis$varfunc2 <- exp(varfunc.ols2$model[1,1])

within_model_containment <- plm(
  model_containment, data = data_bis, model = "within", 
  index=c("Country", "Period"), weights = 1/sqrt(varfunc2))
```

## Final model

```{r}
stargazer(within_model_containment, type="text")
```


# Model for economic support index by productivity for each sector

## Heterogeneity test

First, we test the pooling model versus the within model with the Chow test.

```{r}
model_economic <- EconomicSupportIndex ~ agriculture_forestry_fishing_euro +
  other_service_activities_euro + construction_euro + financial_insurance_euro +
  industry_no_construction_euro + information_communication_euro +
  public_defence_education_health_social_euro +
  professionnal_scientific_technical_administrative_support_euro + 
  real_estate_euro + wholesale_retail_transport_accomodation_food_euro
```

```{r}
pooling_model_economic <- plm(model_economic, data = data_bis, model = "pooling", 
                                index=c("Country", "Period"))
within_model_economic <- plm(model_economic, data = data_bis, model = "within", 
                               index=c("Country", "Period"))
pooltest(pooling_model_economic, within_model_economic)
```

The p-value is strictly below 0.01, so we reject $H_0$, the within model is strictly better than the pooling model.

Now we test the within model against the random effect model using the Hausman test:

```{r}
random_model_economic <- plm(model_economic, data = data_bis, model = "random", 
                               index=c("Country", "Period"))
phtest(within_model_economic, random_model_economic)
```

Because the p-value is lower than 0.01, we reject $H_0$, the within model is strictly better than the random model.

## Heteroskedasticity

Now, we need to check if our within model has heteroskedasticity:

```{r}
bptest(within_model_economic)
```

The p-value is strictly under 0.05, so we reject $H_0$ which means that the variant is not constant accross individuals. We have heteroskedasticity.

We will correct heteroskedasticity:

```{r}
data_bis$residuals_economic <- within_model_economic$residuals
varfunc.ols2 <- plm(log(residuals_economic^2) ~ log(agriculture_forestry_fishing_euro) +
                      log(other_service_activities_euro) + log(construction_euro) +
                      log(financial_insurance_euro) + log(industry_no_construction_euro) +
                      log(information_communication_euro) +
                      log(public_defence_education_health_social_euro) +
                      log(professionnal_scientific_technical_administrative_support_euro) + 
                      log(real_estate_euro) + log(wholesale_retail_transport_accomodation_food_euro),
                    data=data_bis, model="within")

data_bis$varfunc2 <- exp(varfunc.ols2$model[1,1])

within_model_economic <- plm(
  model_economic, data = data_bis, model = "within", 
  index=c("Country", "Period"), weights = 1/sqrt(varfunc2))
```

## Final model

```{r}
stargazer(within_model_economic, type="text")
```


# All the models

```{r}
stargazer(
  within_model_economic, within_model_containment, within_model_government, within_model_stringency,
  type="latex"
  )
```

# Other things done

## Correlation

```{r}
require(corrplot)
require(doParallel)

cl <- detectCores() %>% -1 %>% makeCluster
registerDoParallel(cl)

corrplot(cramer.matrix(data[,-c(24:43)]), type="lower", diag=FALSE, tl.col="black")

stopImplicitCluster()
```

High correlation between variables.

## Graphics for heterogeneity between countries

```{r}
require(gplots)
plotmeans(agriculture_forestry_fishing_euro ~ Country, 
          main="Heterogeineity across countries for agriculture, forestry and fishing",
          data=data_bis)
plotmeans(other_service_activities_euro ~ Country, 
          main="Heterogeineity across countries for other service activities",
          data=data_bis)
plotmeans(construction_euro ~ Country, main="Heterogeineity across countries for construction",
          data=data_bis)
plotmeans(financial_insurance_euro ~ Country, 
          main="Heterogeineity across countries for financial insurance",
          data=data_bis)
plotmeans(industry_no_construction_euro ~ Country, 
          main="Heterogeineity across countries for industry(no construction)",
          data=data_bis)
plotmeans(information_communication_euro ~ Country,
          main="Heterogeineity across countries for information and communication",
          data=data_bis)
plotmeans(professionnal_scientific_technical_administrative_support_euro ~ Country,
          main="Heterogeineity across countries for professionnal, scientific, 
          technical and administrative support", 
          data=data_bis)
plotmeans(public_defence_education_health_social_euro ~ Country, 
          main="Heterogeineity across countries for public, defence, education and health social",
          data=data_bis)
plotmeans(real_estate_euro ~ Country, 
          main="Heterogeineity across countries for real estate",
          data=data_bis)
plotmeans(wholesale_retail_transport_accomodation_food_euro ~ Country, 
          main="Heterogeineity across countries for wholesale, retail, transport and accomodation food", 
          data=data_bis)
```

## Graphics for heterogeneity accross periods

```{r}
require(gplots)
plotmeans(agriculture_forestry_fishing_euro ~ Period, 
          main="Heterogeineity across periods for agriculture, forestry and fishing",
          data=data_bis)
plotmeans(other_service_activities_euro ~ Period, 
          main="Heterogeineity across periods for other service activities",
          data=data_bis)
plotmeans(construction_euro ~ Period, main="Heterogeineity across periods for construction",
          data=data_bis)
plotmeans(financial_insurance_euro ~ Period, 
          main="Heterogeineity across periods for financial insurance",
          data=data_bis)
plotmeans(industry_no_construction_euro ~ Period, 
          main="Heterogeineity across periods for industry(no construction)",
          data=data_bis)
plotmeans(information_communication_euro ~ Period,
          main="Heterogeineity across periods for information and communication",
          data=data_bis)
plotmeans(professionnal_scientific_technical_administrative_support_euro ~ Period,
          main="Heterogeineity across periods for professionnal, scientific, 
          technical and administrative support", 
          data=data_bis)
plotmeans(public_defence_education_health_social_euro ~ Period, 
          main="Heterogeineity across periods for public, defence, education and health social",
          data=data_bis)
plotmeans(real_estate_euro ~ Period, 
          main="Heterogeineity across periods for real estate",
          data=data_bis)
plotmeans(wholesale_retail_transport_accomodation_food_euro ~ Period, 
          main="Heterogeineity across periods for wholesale, retail, transport and accomodation food", 
          data=data_bis)
```

